Supplementary Materials

### 2023-07-13 manuscript/supplementary.tex
ms updates

\subsection{Strong Selection Non-Identifiability}
\label{supp:}

\begin{figure}[htbp]
    \label{suppfig:sel-ident}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/supplementary/ave_sel_vs_pi0.pdf}
  \caption{XXX}
\end{figure}

@@

\subsection{Phastcons Priority, Full Track}
\subsubsection*{CEU}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 280
standard error method: moving block jackknife
negative log-likelihood: 197825873893.4953
number of successful starts: 10000 (100.0% total)
pi_0 = 0.0011279 (0.00113, 0.00113)
pi  = 0.000801495
mut. rate = 2.35e-08  (1.98e-08, 2.72e-08)
Ne = 28,197 (if mu=1e-8), Ne = 14,098 (if mu=2e-8)
R2 = 63.0106% (in-sample)  61.7759% (out-sample)
W = 
        CDS                      gene                     other                    phastcons
------  -----------------------  -----------------------  -----------------------  -----------------------
1e-08   0.000 (-0.0410, 0.0410)  0.901 (0.6521, 1.1503)   0.984 (0.9739, 0.9938)   0.034 (-2.8217, 2.8898)
1e-07   0.000 (-0.1314, 0.1314)  0.026 (-0.2223, 0.2745)  0.000 (-0.0096, 0.0096)  0.376 (-2.4935, 3.2456)
1e-06   0.000 (-0.0088, 0.0088)  0.000 (-0.0018, 0.0027)  0.000 (-0.0001, 0.0001)  0.001 (-0.0308, 0.0318)
1e-05   0.000 (-0.0002, 0.0002)  0.019 (0.0133, 0.0249)   0.000 (-0.0000, 0.0000)  0.000 (-0.0003, 0.0003)
0.0001  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)
0.001   0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.472 (0.4050, 0.5388)
0.01    0.000 (-0.0001, 0.0001)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.046 (0.0351, 0.0571)
0.1     1.000 (0.8620, 1.1380)   0.053 (0.0454, 0.0608)   0.016 (0.0138, 0.0185)   0.071 (0.0571, 0.0858)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{CHB}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 280
standard error method: moving block jackknife
negative log-likelihood: 61821783504.67356
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00106467 (0.00106, 0.00107)
pi  = 0.000752601
mut. rate = 2.557e-08  (-8.06e-10, 5.2e-08)
Ne = 26,616 (if mu=1e-8), Ne = 13,308 (if mu=2e-8)
R2 = 61.0847% (in-sample)  59.2923% (out-sample)
W = 
        CDS                      gene                     other                    phastcons
------  -----------------------  -----------------------  -----------------------  -----------------------
1e-08   0.000 (-0.5839, 0.5839)  0.931 (0.6381, 1.2238)   0.985 (0.9661, 1.0044)   0.478 (-2.5565, 3.5128)
1e-07   0.000 (-0.2506, 0.2506)  0.005 (-0.2858, 0.2949)  0.000 (-0.0165, 0.0165)  0.002 (-3.0192, 3.0225)
1e-06   0.000 (-0.0119, 0.0119)  0.000 (-0.0043, 0.0045)  0.000 (-0.0002, 0.0002)  0.000 (-0.0172, 0.0177)
1e-05   0.000 (-0.0001, 0.0001)  0.013 (-0.0013, 0.0268)  0.000 (-0.0000, 0.0000)  0.000 (-0.0002, 0.0002)
0.0001  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)
0.001   0.000 (-0.0000, 0.0000)  0.003 (0.0005, 0.0049)   0.000 (-0.0000, 0.0000)  0.430 (0.1533, 0.7071)
0.01    0.000 (-0.0001, 0.0001)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.090 (0.0316, 0.1477)
0.1     1.000 (0.3574, 1.6426)   0.049 (0.0174, 0.0804)   0.015 (0.0053, 0.0243)   0.000 (-0.0005, 0.0005)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{YRI}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 280
standard error method: moving block jackknife
negative log-likelihood: 250656989872.19766
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00147277 (0.00147, 0.00147)
pi  = 0.00106447
mut. rate = 1.708e-08  (-4.08e-08, 7.49e-08)
Ne = 36,819 (if mu=1e-8), Ne = 18,409 (if mu=2e-8)
R2 = 68.1177% (in-sample)  68.1947% (out-sample)
W = 
        CDS                      gene                     other                    phastcons
------  -----------------------  -----------------------  -----------------------  -----------------------
1e-08   1.000 (-3.4930, 5.4930)  0.902 (0.6716, 1.1325)   0.979 (0.9416, 1.0156)   0.000 (-1.2400, 1.2407)
1e-07   0.000 (-4.4936, 4.4936)  0.000 (-0.1820, 0.1820)  0.000 (-0.0194, 0.0194)  0.004 (-0.5459, 0.5537)
1e-06   0.000 (-0.0107, 0.0107)  0.000 (-0.0024, 0.0024)  0.000 (-0.0003, 0.0003)  0.001 (-0.0353, 0.0365)
1e-05   0.000 (-0.0001, 0.0001)  0.042 (-0.0177, 0.1024)  0.000 (-0.0000, 0.0000)  0.000 (-0.0005, 0.0006)
0.0001  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0001, 0.0001)
0.001   0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.523 (-0.2146, 1.2611)
0.01    0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.212 (-0.0866, 0.5104)
0.1     0.000 (-0.0006, 0.0006)  0.056 (-0.0228, 0.1339)  0.021 (-0.0088, 0.0516)  0.260 (-0.1070, 0.6270)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsection{Phastcons Priority, Sparse Track}
\subsubsection*{CEU}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
standard error method: None
negative log-likelihood: 197826612684.87143
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00112308
pi  = 0.000801495
mut. rate = 2.019e-08 
Ne = 28,076 (if mu=1e-8), Ne = 14,038 (if mu=2e-8)
R2 = 63.0152% (in-sample)  61.9834% (out-sample)
W = 
          CDS    gene    phastcons
------  -----  ------  -----------
1e-08   0       0.913        0.227
1e-07   0       0            0.004
1e-06   0.004   0            0
1e-05   0       0.019        0
0.0001  0       0            0
0.001   0       0            0.546
0.01    0       0            0.061
0.1     0.996   0.069        0.161
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{CHB}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
standard error method: None
negative log-likelihood: 61822016128.79776
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00106069
pi  = 0.000752601
mut. rate = 5.887e-08 
Ne = 26,517 (if mu=1e-8), Ne = 13,258 (if mu=2e-8)
R2 = 61.0804% (in-sample)  59.4419% (out-sample)
W = 
          CDS    gene    phastcons
------  -----  ------  -----------
1e-08   0.617   0.968        0.744
1e-07   0.01    0            0.02
1e-06   0       0            0
1e-05   0       0.005        0
0.0001  0       0            0
0.001   0       0.001        0.185
0.01    0       0            0.051
0.1     0.373   0.026        0
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{YRI}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
standard error method: None
negative log-likelihood: 250657908564.79294
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00146801
pi  = 0.00106447
mut. rate = 1.864e-08 
Ne = 36,700 (if mu=1e-8), Ne = 18,350 (if mu=2e-8)
R2 = 68.1582% (in-sample)  68.4462% (out-sample)
W = 
          CDS    gene    phastcons
------  -----  ------  -----------
1e-08       1   0.907        0
1e-07       0   0.001        0
1e-06       0   0            0
1e-05       0   0.035        0
0.0001      0   0            0
0.001       0   0            0.477
0.01        0   0            0.199
0.1         0   0.057        0.323
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsection{Feature Priority, Full Track}
\subsubsection*{CEU}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 457
standard error method: moving block jackknife
negative log-likelihood: 197848627167.32043
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00115698 (0.00116, 0.00116)
pi  = 0.000801495
mut. rate = 4.1e-08  (2.2e-08, 6e-08)
Ne = 28,924 (if mu=1e-8), Ne = 14,462 (if mu=2e-8)
R2 = 60.3026% (in-sample)  58.5808% (out-sample)
W = 
        CDS                      gene                     other                    phastcons
------  -----------------------  -----------------------  -----------------------  -----------------------
1e-08   0.107 (-1.0244, 1.2375)  0.946 (0.7974, 1.0947)   1.000 (0.9991, 1.0009)   0.000 (-0.2751, 0.2757)
1e-07   0.000 (-1.0319, 1.0319)  0.001 (-0.1448, 0.1458)  0.000 (-0.0009, 0.0009)  0.000 (-0.2482, 0.2482)
1e-06   0.000 (-0.0087, 0.0087)  0.000 (-0.0013, 0.0021)  0.000 (-0.0000, 0.0000)  0.000 (-0.0150, 0.0150)
1e-05   0.000 (-0.0001, 0.0001)  0.023 (0.0088, 0.0368)   0.000 (-0.0000, 0.0000)  0.000 (-0.0003, 0.0003)
0.0001  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)
0.001   0.144 (0.0831, 0.2059)   0.014 (0.0080, 0.0196)   0.000 (-0.0000, 0.0000)  0.229 (0.1327, 0.3256)
0.01    0.000 (-0.0012, 0.0012)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.086 (0.0462, 0.1253)
0.1     0.749 (0.4358, 1.0622)   0.016 (0.0095, 0.0233)   0.000 (-0.0000, 0.0000)  0.685 (0.3987, 0.9709)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{CHB}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 454
standard error method: moving block jackknife
negative log-likelihood: 61827828856.16418
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00108991 (0.00109, 0.00109)
pi  = 0.000752601
mut. rate = 3.755e-08  (1.55e-08, 5.96e-08)
Ne = 27,247 (if mu=1e-8), Ne = 13,623 (if mu=2e-8)
R2 = 58.7328% (in-sample)  56.4805% (out-sample)
W = 
        CDS                      gene                     other                    phastcons
------  -----------------------  -----------------------  -----------------------  -----------------------
1e-08   0.088 (-0.9233, 1.0989)  0.940 (0.7665, 1.1139)   1.000 (0.9988, 1.0012)   0.006 (-0.3608, 0.3730)
1e-07   0.010 (-0.8568, 0.8763)  0.000 (-0.1685, 0.1691)  0.000 (-0.0011, 0.0011)  0.003 (-0.2610, 0.2674)
1e-06   0.000 (-0.0075, 0.0078)  0.000 (-0.0021, 0.0021)  0.000 (-0.0000, 0.0000)  0.000 (-0.0145, 0.0151)
1e-05   0.000 (-0.0001, 0.0001)  0.023 (0.0037, 0.0422)   0.000 (-0.0000, 0.0000)  0.000 (-0.0003, 0.0003)
0.0001  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)
0.001   0.156 (0.0732, 0.2384)   0.017 (0.0081, 0.0260)   0.000 (-0.0000, 0.0000)  0.244 (0.1185, 0.3696)
0.01    0.000 (-0.0139, 0.0140)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.254 (0.1215, 0.3871)
0.1     0.746 (0.3590, 1.1338)   0.020 (0.0094, 0.0298)   0.000 (-0.0000, 0.0000)  0.492 (0.2392, 0.7448)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{YRI}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 280
standard error method: moving block jackknife
negative log-likelihood: 250679665159.79324
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00151818 (0.00152, 0.00152)
pi  = 0.00106447
mut. rate = 4.195e-08  (2.76e-08, 5.63e-08)
Ne = 37,954 (if mu=1e-8), Ne = 18,977 (if mu=2e-8)
R2 = 65.5097% (in-sample)  64.9049% (out-sample)
W = 
        CDS                      gene                     other                    phastcons
------  -----------------------  -----------------------  -----------------------  -----------------------
1e-08   0.364 (-0.4599, 1.1874)  0.931 (0.8360, 1.0260)   1.000 (0.9993, 1.0007)   0.003 (-0.1973, 0.2040)
1e-07   0.001 (-0.7930, 0.7942)  0.000 (-0.0901, 0.0901)  0.000 (-0.0007, 0.0007)  0.000 (-0.1669, 0.1675)
1e-06   0.000 (-0.0038, 0.0040)  0.000 (-0.0009, 0.0009)  0.000 (-0.0000, 0.0000)  0.000 (-0.0106, 0.0109)
1e-05   0.000 (-0.0001, 0.0001)  0.039 (0.0240, 0.0532)   0.000 (-0.0000, 0.0000)  0.000 (-0.0002, 0.0002)
0.0001  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)
0.001   0.091 (0.0617, 0.1212)   0.011 (0.0077, 0.0150)   0.000 (-0.0000, 0.0000)  0.151 (0.1030, 0.1986)
0.01    0.000 (-0.0001, 0.0001)  0.000 (-0.0001, 0.0001)  0.000 (-0.0000, 0.0000)  0.328 (0.2249, 0.4316)
0.1     0.544 (0.3725, 0.7157)   0.019 (0.0130, 0.0250)   0.000 (-0.0000, 0.0000)  0.517 (0.3548, 0.6796)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsection{Feature Priority, Sparse Track}
\subsubsection*{CEU}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 27
standard error method: moving block jackknife
negative log-likelihood: 197848626646.91736
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00115698 (0.00116, 0.00116)
pi  = 0.000801495
mut. rate = 4.104e-08  (3.87e-08, 4.34e-08)
Ne = 28,924 (if mu=1e-8), Ne = 14,462 (if mu=2e-8)
R2 = 60.3027% (in-sample)  58.5823% (out-sample)
W = 
        CDS                      gene                     phastcons
------  -----------------------  -----------------------  -----------------------
1e-08   0.107 (0.0490, 0.1649)   0.947 (0.9402, 0.9539)   0.001 (-0.0478, 0.0491)
1e-07   0.000 (-0.0273, 0.0279)  0.000 (-0.0052, 0.0052)  0.000 (-0.0073, 0.0075)
1e-06   0.000 (-0.0003, 0.0006)  0.000 (-0.0001, 0.0001)  0.001 (-0.0008, 0.0019)
1e-05   0.000 (-0.0000, 0.0000)  0.023 (0.0187, 0.0268)   0.000 (-0.0000, 0.0000)
0.0001  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)
0.001   0.144 (0.1365, 0.1522)   0.014 (0.0130, 0.0146)   0.229 (0.2150, 0.2428)
0.01    0.000 (-0.0001, 0.0001)  0.000 (-0.0000, 0.0000)  0.086 (0.0733, 0.0981)
0.1     0.748 (0.7078, 0.7887)   0.016 (0.0155, 0.0173)   0.684 (0.6463, 0.7219)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{CHB}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 26
standard error method: moving block jackknife
negative log-likelihood: 61827828699.43107
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00108991 (0.00109, 0.00109)
pi  = 0.000752601
mut. rate = 3.719e-08  (3.2e-08, 4.24e-08)
Ne = 27,247 (if mu=1e-8), Ne = 13,623 (if mu=2e-8)
R2 = 58.7329% (in-sample)  56.4805% (out-sample)
W = 
        CDS                      gene                     phastcons
------  -----------------------  -----------------------  -----------------------
1e-08   0.089 (-0.0565, 0.2340)  0.938 (0.9196, 0.9573)   0.000 (-0.1223, 0.1223)
1e-07   0.000 (-0.0861, 0.0861)  0.001 (-0.0154, 0.0180)  0.000 (-0.0145, 0.0146)
1e-06   0.000 (-0.0005, 0.0010)  0.000 (-0.0001, 0.0002)  0.000 (-0.0009, 0.0009)
1e-05   0.000 (-0.0000, 0.0000)  0.023 (0.0203, 0.0260)   0.000 (-0.0000, 0.0000)
0.0001  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)
0.001   0.157 (0.1380, 0.1766)   0.017 (0.0151, 0.0194)   0.246 (0.2161, 0.2767)
0.01    0.000 (-0.0004, 0.0006)  0.000 (-0.0000, 0.0000)  0.257 (0.2252, 0.2883)
0.1     0.754 (0.6611, 0.8461)   0.020 (0.0173, 0.0222)   0.497 (0.4358, 0.5578)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{YRI}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 17
standard error method: moving block jackknife
negative log-likelihood: 250679664591.4161
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00151817 (0.00152, 0.00152)
pi  = 0.00106447
mut. rate = 4.179e-08  (3.84e-08, 4.52e-08)
Ne = 37,954 (if mu=1e-8), Ne = 18,977 (if mu=2e-8)
R2 = 65.5099% (in-sample)  64.9049% (out-sample)
W = 
        CDS                      gene                     phastcons
------  -----------------------  -----------------------  -----------------------
1e-08   0.360 (0.3063, 0.4146)   0.931 (0.9239, 0.9375)   0.000 (-0.0647, 0.0647)
1e-07   0.002 (-0.0234, 0.0265)  0.000 (-0.0051, 0.0052)  0.000 (-0.0097, 0.0097)
1e-06   0.000 (-0.0003, 0.0003)  0.000 (-0.0000, 0.0001)  0.000 (-0.0009, 0.0009)
1e-05   0.000 (-0.0000, 0.0000)  0.039 (0.0359, 0.0417)   0.000 (-0.0000, 0.0000)
0.0001  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)
0.001   0.092 (0.0849, 0.0987)   0.011 (0.0105, 0.0122)   0.151 (0.1401, 0.1627)
0.01    0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)  0.329 (0.3048, 0.3540)
0.1     0.546 (0.5054, 0.5870)   0.019 (0.0176, 0.0205)   0.519 (0.4804, 0.5580)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsection{CADD 6\%, Full Track}
\subsubsection*{CEU}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 280
standard error method: moving block jackknife
negative log-likelihood: 197826953189.02365
number of successful starts: 20000 (100.0% total)
pi_0 = 0.00109999 (0.00110, 0.00110)
pi  = 0.000801495
mut. rate = 1.537e-08  (8e-09, 2.27e-08)
Ne = 27,499 (if mu=1e-8), Ne = 13,749 (if mu=2e-8)
R2 = 62.9394% (in-sample)  61.7433% (out-sample)
W = 
        cadd6                    other
------  -----------------------  -----------------------
1e-08   0.000 (-0.2792, 0.2795)  0.965 (0.9473, 0.9832)
1e-07   0.000 (-0.2355, 0.2355)  0.000 (-0.0109, 0.0109)
1e-06   0.000 (-0.0371, 0.0371)  0.000 (-0.0001, 0.0001)
1e-05   0.000 (-0.0011, 0.0013)  0.000 (-0.0000, 0.0000)
0.0001  0.026 (0.0129, 0.0393)   0.000 (-0.0000, 0.0000)
0.001   0.555 (0.3257, 0.7834)   0.000 (-0.0000, 0.0000)
0.01    0.000 (-0.0001, 0.0001)  0.000 (-0.0000, 0.0000)
0.1     0.419 (0.2460, 0.5921)   0.035 (0.0204, 0.0491)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{CHB}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 280
standard error method: moving block jackknife
negative log-likelihood: 61821323176.26884
number of successful starts: 20000 (100.0% total)
pi_0 = 0.00103624 (0.00104, 0.00104)
pi  = 0.000752601
mut. rate = 1.508e-08  (-2.43e-09, 3.26e-08)
Ne = 25,905 (if mu=1e-8), Ne = 12,952 (if mu=2e-8)
R2 = 61.3115% (in-sample)  59.6228% (out-sample)
W = 
        cadd6                    other
------  -----------------------  -----------------------
1e-08   0.000 (-0.6278, 0.6278)  0.961 (0.9187, 1.0036)
1e-07   0.007 (-0.4928, 0.5076)  0.000 (-0.0227, 0.0227)
1e-06   0.009 (-0.0393, 0.0570)  0.000 (-0.0002, 0.0002)
1e-05   0.000 (-0.0014, 0.0015)  0.000 (-0.0000, 0.0000)
0.0001  0.004 (-0.0082, 0.0171)  0.000 (-0.0000, 0.0000)
0.001   0.670 (0.0898, 1.2509)   0.000 (-0.0000, 0.0000)
0.01    0.000 (-0.0001, 0.0001)  0.000 (-0.0000, 0.0000)
0.1     0.309 (0.0412, 0.5766)   0.039 (0.0051, 0.0726)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{YRI}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 280
standard error method: moving block jackknife
negative log-likelihood: 250659830283.90668
number of successful starts: 20000 (100.0% total)
pi_0 = 0.00145893 (0.00146, 0.00146)
pi  = 0.00106447
mut. rate = 1.461e-08  (8.61e-09, 2.06e-08)
Ne = 36,473 (if mu=1e-8), Ne = 18,236 (if mu=2e-8)
R2 = 68.0839% (in-sample)  68.0751% (out-sample)
W = 
        cadd6                    other
------  -----------------------  -----------------------
1e-08   0.000 (-0.2318, 0.2327)  0.958 (0.9399, 0.9768)
1e-07   0.023 (-0.2328, 0.2797)  0.000 (-0.0083, 0.0089)
1e-06   0.001 (-0.0153, 0.0176)  0.000 (-0.0001, 0.0001)
1e-05   0.000 (-0.0003, 0.0004)  0.000 (-0.0000, 0.0000)
0.0001  0.065 (0.0378, 0.0921)   0.000 (-0.0000, 0.0000)
0.001   0.407 (0.2491, 0.5649)   0.000 (-0.0000, 0.0000)
0.01    0.078 (0.0439, 0.1126)   0.000 (-0.0000, 0.0000)
0.1     0.425 (0.2604, 0.5891)   0.041 (0.0253, 0.0573)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsection{CADD 6\%, Sparse Track}
\subsubsection*{CEU}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
standard error method: None
negative log-likelihood: 197829116669.21103
number of successful starts: 20000 (100.0% total)
pi_0 = 0.00107623
pi  = 0.000801495
mut. rate = 2.121e-08 
Ne = 26,905 (if mu=1e-8), Ne = 13,452 (if mu=2e-8)
R2 = 62.8555% (in-sample)  61.6574% (out-sample)
W = 
          cadd6
------  -------
1e-08     0
1e-07     0
1e-06     0
1e-05     0
0.0001    0.014
0.001     0.408
0.01      0
0.1       0.578
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{CHB}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
standard error method: None
negative log-likelihood: 61822132892.58568
number of successful starts: 20000 (100.0% total)
pi_0 = 0.00101201
pi  = 0.000752601
mut. rate = 2.124e-08 
Ne = 25,300 (if mu=1e-8), Ne = 12,650 (if mu=2e-8)
R2 = 61.2064% (in-sample)  59.5382% (out-sample)
W = 
          cadd6
------  -------
1e-08     0
1e-07     0
1e-06     0
1e-05     0
0.0001    0
0.001     0.477
0.01      0
0.1       0.523
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{YRI}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
standard error method: None
negative log-likelihood: 250663447300.65836
number of successful starts: 20000 (100.0% total)
pi_0 = 0.00142415
pi  = 0.00106447
mut. rate = 2.091e-08 
Ne = 35,603 (if mu=1e-8), Ne = 17,801 (if mu=2e-8)
R2 = 68.028% (in-sample)  68.0414% (out-sample)
W = 
          cadd6
------  -------
1e-08     0
1e-07     0
1e-06     0
1e-05     0
0.0001    0.038
0.001     0.302
0.01      0.033
0.1       0.627
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsection{CADD 6\%, Full Track}
\subsubsection*{CEU}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 140
standard error method: moving block jackknife
negative log-likelihood: 197834651568.3971
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00109606 (0.00110, 0.00110)
pi  = 0.000801495
mut. rate = 1.157e-08  (9.01e-09, 1.41e-08)
Ne = 27,401 (if mu=1e-8), Ne = 13,700 (if mu=2e-8)
R2 = 62.1245% (in-sample)  60.8009% (out-sample)
W = 
        cadd8                    other
------  -----------------------  -----------------------
1e-08   0.000 (-0.0835, 0.0835)  0.952 (0.9415, 0.9624)
1e-07   0.004 (-0.1451, 0.1523)  0.000 (-0.0043, 0.0043)
1e-06   0.000 (-0.0145, 0.0150)  0.000 (-0.0001, 0.0001)
1e-05   0.000 (-0.0005, 0.0005)  0.000 (-0.0000, 0.0000)
0.0001  0.052 (0.0393, 0.0656)   0.000 (-0.0000, 0.0000)
0.001   0.537 (0.4316, 0.6417)   0.000 (-0.0000, 0.0000)
0.01    0.000 (-0.0000, 0.0000)  0.000 (-0.0000, 0.0000)
0.1     0.407 (0.3276, 0.4867)   0.048 (0.0386, 0.0575)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{CHB}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 140
standard error method: moving block jackknife
negative log-likelihood: 61823378586.32404
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00103245 (0.00103, 0.00103)
pi  = 0.000752601
mut. rate = 1.113e-08  (4.22e-09, 1.8e-08)
Ne = 25,811 (if mu=1e-8), Ne = 12,905 (if mu=2e-8)
R2 = 60.6265% (in-sample)  58.8768% (out-sample)
W = 
        cadd8                    other
------  -----------------------  -----------------------
1e-08   0.000 (-0.3716, 0.3716)  0.944 (0.9141, 0.9736)
1e-07   0.000 (-0.2895, 0.2903)  0.001 (-0.0075, 0.0094)
1e-06   0.000 (-0.0376, 0.0378)  0.000 (-0.0001, 0.0001)
1e-05   0.000 (-0.0005, 0.0005)  0.000 (-0.0000, 0.0000)
0.0001  0.026 (0.0069, 0.0447)   0.000 (-0.0000, 0.0000)
0.001   0.690 (0.3451, 1.0351)   0.000 (-0.0000, 0.0000)
0.01    0.000 (-0.0001, 0.0001)  0.000 (-0.0000, 0.0000)
0.1     0.284 (0.1418, 0.4254)   0.055 (0.0275, 0.0829)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{YRI}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 140
standard error method: moving block jackknife
negative log-likelihood: 250669695762.61414
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00145867 (0.00146, 0.00146)
pi  = 0.00106447
mut. rate = 1.013e-08  (5.65e-09, 1.46e-08)
Ne = 36,466 (if mu=1e-8), Ne = 18,233 (if mu=2e-8)
R2 = 67.1076% (in-sample)  66.9835% (out-sample)
W = 
        cadd8                    other
------  -----------------------  -----------------------
1e-08   0.000 (-0.3206, 0.3212)  0.932 (0.9054, 0.9583)
1e-07   0.002 (-0.1725, 0.1762)  0.000 (-0.0062, 0.0062)
1e-06   0.000 (-0.0130, 0.0130)  0.000 (-0.0001, 0.0001)
1e-05   0.000 (-0.0004, 0.0004)  0.000 (-0.0000, 0.0000)
0.0001  0.103 (0.0627, 0.1425)   0.000 (-0.0000, 0.0000)
0.001   0.438 (0.2744, 0.6008)   0.000 (-0.0000, 0.0000)
0.01    0.000 (-0.0003, 0.0003)  0.000 (-0.0000, 0.0000)
0.1     0.458 (0.2870, 0.6282)   0.068 (0.0427, 0.0936)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsection{CADD 6\%, Sparse Track}
\subsubsection*{CEU}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

ML estimates: (whole genome)
number jackknife samples: 140
standard error method: moving block jackknife
negative log-likelihood: 197836763801.90414
number of successful starts: 10000 (100.0% total)
pi_0 = 0.00107057 (0.00107, 0.00107)
pi  = 0.000801495
mut. rate = 1.603e-08  (1.57e-08, 1.63e-08)
Ne = 26,764 (if mu=1e-8), Ne = 13,382 (if mu=2e-8)
R2 = 62.061% (in-sample)  60.5937% (out-sample)
W = 
        cadd8
------  -----------------------
1e-08   0.000 (-0.0171, 0.0171)
1e-07   0.000 (-0.0007, 0.0007)
1e-06   0.000 (-0.0000, 0.0000)
1e-05   0.000 (-0.0000, 0.0000)
0.0001  0.032 (0.0268, 0.0372)
0.001   0.400 (0.3894, 0.4110)
0.01    0.000 (-0.0000, 0.0000)
0.1     0.568 (0.5575, 0.5781)
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{CHB}
\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}

>>>>

\subsection{Strong Selection Grids}
\label{supp:strong-sel-grid}

\begin{figure}[htbp]
    \label{suppfig:strong-sel-dfe}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/supplementary/strongsel_grid_dfe.pdf}
  \caption{The DFE estimates for the strong selection grid (up to $s=10^{-1}$).}
\end{figure}

\begin{figure}[htbp]
    \label{suppfig:sel-ident}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/supplementary/ave_sel_vs_pi0.pdf}

  \caption{The maximum likelihood estimates of $\pi_0$ and average selection
  coefficient implied by the estimated DFE for the CADD 6\% models. Diamonds
indicate estimates under the strong selection grid (up to $s=10^{-1}$) and
circles indicate estimates under the default grid (up to $s=10^{-2}$).}

@@
